A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex

A major problem with any transit search is the potential confusion
between transiting planets and stellar eclipsing binaries.  Of
particular concern are grazing stellar eclipses or stellar eclipses
that contribute only a small fraction of the total light in a target
star's photometric aperture, thus display greatly diluted eclipse
depths able to mimic the signals of small planets.

>>>>

A major problem with any transit search is the potential confusion
between transiting planets and stellar eclipsing binaries.  Of
particular concern are grazing stellar eclipses or stellar eclipses
that contribute only a small fraction of the total light in a
photometric aperture, resulting in greatly diluted eclipse depths able
to mimic the signals of small planets.
